---
title: "数据清洗III"
author: "Leopard"
date: "2/14/2020"
output:
  html_document:
    self_contained: false
    theme: united
    highlight: tango
---

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
      font-family:Noto Nastaliq Urdu;
  }
td {  /* Table  */
  font-size: 16px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkRed;
  font-family:Noto Nastaliq Urdu;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkRed;
  font-family:Noto Nastaliq Urdu;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
}
code.r{ /* Code block */
    font-size: 18px;
    font-family:Noto Nastaliq Urdu;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 18px;
    font-family:Noto Nastaliq Urdu;
}
</style>
```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
```


```{r setup, include=FALSE}
knitr::knit_hooks$set(error = function(x, options) {
  paste0("<pre style=\"color: red;\"><code>", x, "</code></pre>")
})
knitr::opts_chunk$set(echo = TRUE)
```

#分类变量处理

```{r}
head(esoph)
```

##计数
```{r}
table(esoph$agegp,esoph$alcgp)
```

```{r}
table(esoph$alcgp,esoph$tobgp,esoph$agegp)
```

```{r}
table(iris$Sepal.Length>7.0,iris$Species)
```

```{r}
addmargins(table(iris$Sepal.Length>7.0,iris$Species),FUN = sum,
          margin = c(1,2))
```

```{r}
prop.table(table(iris$Sepal.Length>7.0,iris$Species),
           margin = 1)
```

```{r}
xtabs(ncontrols~agegp+alcgp,data=esoph)
##根据ncontrols来计数
```

##改变因子水平标签
```{r}
gss_cat %>% count(partyid)
```

```{r}
gss_cat %>%
mutate(partyid = fct_recode(partyid,
"Republican, strong" = "Strong republican",
"Republican, weak" = "Not str republican",
"Independent, near rep" = "Ind,near rep",
"Independent, near dem" = "Ind,near dem",
"Democrat, weak" = "Not str democrat",
"Democrat, strong" = "Strong democrat"
)) %>%
count(partyid)
```

##改变因子水平
```{r}
gss_cat %>%
mutate(partyid = fct_recode(partyid,
"Republican, strong" = "Strong republican",
"Republican, weak" = "Not str republican",
"Independent, near rep" = "Ind,near rep",
"Independent, near dem" = "Ind,near dem",
"Democrat, weak" = "Not str democrat",
"Democrat, strong" = "Strong democrat",
"Other" = "No answer",
"Other" = "Don't know",
"Other" = "Other party"
)) %>%
  count(partyid)
```

##合并因子水平
```{r}
gss_cat %>%
mutate(partyid = fct_collapse(partyid,
other = c("No answer", "Don't know", "Other party"),
rep = c("Strong republican", "Not str republican"),
ind = c("Ind,near rep", "Independent", "Ind,near dem"),
dem = c("Not str democrat", "Strong democrat")
)) %>%
count(partyid)
```





