---
title: "数据清洗5"
author: "Leopard"
date: "2/14/2020"
output:
  html_document:
    self_contained: false
    theme: united
    highlight: tango
---
<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
      font-family:Noto Nastaliq Urdu;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkRed;
  font-family:Noto Nastaliq Urdu;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkRed;
  font-family:Noto Nastaliq Urdu;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
}
code.r{ /* Code block */
    font-size: 18px;
    font-family:Noto Nastaliq Urdu;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 18px;
    font-family:Noto Nastaliq Urdu;
}
</style>

```{r setup, include=FALSE}
knitr::knit_hooks$set(error = function(x, options) {
  paste0("<pre style=\"color: red;\"><code>", x, "</code></pre>")
})
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#时间日期数据处理

```{r,message=FALSE}
library(lubridate)
```

##解析
```{r}
date7 <- c("Feb272009", "Jan272009")
as.Date(date7, "%b%d%Y") 
```

```{r}
mdy(c("Feb272009", "Jan272009"))
```

```{r}
ymd(c("2010-10-10", "20200202",'2020 January 2','2018/Jan/01',
      '19/12/10','181010'))
```

##信息提取
```{r}
datetime <- ymd_hms("2016-07-08 12:34:56")
year(datetime)
month(datetime)
mday(datetime)
yday(datetime)
wday(datetime)
```

##计算时间间隔
```{r}
l_age <- today() - ymd(19920513)
l_age
```

##间隔
```{r}
as.duration(l_age)
```

```{r}
dweeks(5)
dyears(2)
```

```{r}
dyears(1) + dweeks(12) + dhours(15)
```

##区段

```{r}
10 * (months(6) + days(1))
```

```{r}
ymd("2016-01-01") + dyears(1)
ymd("2016-01-01") + years(1)
```

##实例

```{r}
df <- tibble(ids = c('410112198210190809',
                     '232011198211180103',
                     '340822199408221822',
                     '102211199801032328'))
df <- df %>% mutate(age = ymd('2020-01-01')-ymd(str_sub(ids,7,14))) %>%
  mutate(age = time_length(age,unit = 'year'))
df
```










